---
title: Git Demonstration
date: 11-26-2024
format: html
    # pdf:
    #     documentclass: article
    #     papersize: letter
    #     mainfont: Times New Roman
author:
    - name: 
        given: Gage
        family: Rowden
      id: GR
      orcid: 0000-0002-7517-0480
      email: rowde002@umn.edu
      affiliation:
          name: University of Minnesota
          city: Saint Paul
          state: MN
      corresponding: true

    - name: 
        given: Sarah
        family: Gresch
      id: SG
      orcid: 0000-0002-7517-0481
      email: rowde002@umn.edu
      affiliation:
          name: University of Minnesota
          city: Saint Paul
          state: MN
      corresponding: true

    - name: Albert Einstein
      orcid: 0000-0000-0000-0001
      email: email-not-invented@aol.com
      affiliation:
          name: Princeton University
          city: Newark
          state: NJ
abstract: Three  Rings  for  the  Elven-kings  under  the  sky, Seven  for  the  Dwarf-lords  in  their  halls  of  stone, Nine  for  Mortal  Men  doomed  to  die, One  for  the  Dark  Lord  on  his  dark  throne In  the  Land  of  Mordor  where  the  Shadows  lie. One  Ring  to  rule  them  all,  One  Ring  to  find  them, One  Ring  to  bring  them  all  and  in  the  darkness  bind  them In  the  Land  of  Mordor  where  the  Shadows  lie. 
keywords: [git, github, Quarto]
bibliography:
    references.bib
bibliographystyle: 
    apa
---
<!-- # Git Demonstration

#### Authors
Gage Rowden<sup>1</sup>, Second Author<sup>2</sup>

#### Affiliations
<sup>1</sup>University of Minnesota\
<sup>2</sup>Colorado State University

## Abstract
Yada yada. -->




## Introduction
fuck

‘This,’  he  says,  ‘is  the  one  art  that  we  can  certainly  claim to  be  our  own  invention.  When  Hobbits  first  began  to  smoke is  not  known,  all  the  legends  and  family  histories  take  it  for granted;  for  ages  folk  in  the  Shire  smoked  various  herbs,  some fouler,  some  sweeter.  But  all  accounts  agree  that  Tobold Hornblower  of  Longbottom  in  the  Southfarthing  first  grew the  true  pipe-weed  in  his  gardens  in  the  days  of  Isengrim  the Second,  about  the  year  1070  of  Shire -reckoning.  The  best home-grown  still  comes  from  that  district,  especially  the varieties  now  known  as  Longbottom  Leaf,  Old  Toby,  and Southern  Star. 

‘How  Old  Toby  came  by  the  plant  is  not  recorded,  for  to his  dying  day  he  would  not  tell.  He  knew  much  about  herbs, but  he  was  no  traveller.  It  is  said  that  in  his  youth  he  went often  to  Bree,  though  he  certainly  never  went  further  from the  Shire  than  that.  It  is  thus  quite  possible  that  he  learned of  this  plant  in  Bree,  where  now,  at  any  rate,  it  grows  well  on the  south  slopes  of  the  hill.  The  Bree-hobbits  claim  to  have been  the  first  actual  smokers  of  the  pipe-weed.  They  claim, of  course,  to  have  done  everything  before  the  people  of  the Shire,  whom  they  refer  to  as  “colonists”;  but  in  this  case  their claim  is,  I  think,  likely  to  be  true.  And  certainly  it  was  from Bree  that  the  art  of  smoking  the  genuine  weed  spread  in the  recent  centuries  among  Dwarves  and  such  other  folk, Rangers,  Wizards,  or  wanderers,  as  still  passed  to  and  fro through  that  ancient  road-meeting.  The  home  and  centre  of the  art  is  thus  to  be  found  in  the  old  inn  of  Bree,  The  Prancing Pony,  that  has  been  kept  by  the  family  of  Butterbur  from time  beyond  record. 

‘All  the  same,  observations  that  I  have  made  on  my  own many  journeys  south  have  convinced  me  that  the  weed  itself is  not  native  to  our  parts  of  the  world,  but  came  northward from  the  lower  Anduin,  whither  it  was,  I  suspect,  originally brought  over  Sea  by  the  Men  of  Westernesse.  It  grows  abund¬ antly  in  Gondor,  and  there  is  richer  and  larger  than  in  the North,  where  it  is  never  found  wild,  and  flourishes  only  in warm  sheltered  places  like  Longbottom.  The  Men  of  Gondor call  it  sweet  galenas,  and  esteem  it  only  for  the  fragrance  of  its flowers.  From  that  land  it  must  have  been  carried  up  the Greenway  during  the  long  centuries  between  the  coming  of Elendil  and  our  own  days.  But  even  the  Dunedain  of  Gondor allow  us  this  credit:  Hobbits  first  put  it  into  pipes.  Not  even the  Wizards  first  thought  of  that  before  we  did.  Though  one Wizard  that  I  knew  took  up  the  art  long  ago,  and  became  as skilful  in  it  as  in  all  other  things  that  he  put  his  mind  to.’ 

## Materials & Methods

### RT-QuIC
RT-QuIC was performed like it should be according to @Schwabenlander2021.

### Statistical Analysis
We did the stats like we always have.\
We used MPR, described in @Rowden2023.

## Results

| **Sample** | **MPR** | **RAF** | **p-value** |  **Result**  |
|:----------:|:-------:|:-------:|:-----------:|:------------:|
|      1     |    12   |    .4   |     .001    |   Detected   |
|      2     |    2    |   .005  |     .12     |    Suspect   |
|      3     |   1.8   |    0    |     .999    | Not Detected |

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(kableExtra)

kable(mtcars, "html")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
#| label: fig-cap
#| layout-ncol: 2
#| fig-cap:
#|  - "MPG vs cylinders"
#|  - "Displacement vs weight"
#| cap-location: bottom

library(tidyverse)

mtcars %>%
  ggplot(aes(x = cyl, y = mpg)) +
    geom_point(size = 3, position = position_jitter(width = 0.05)) +
    geom_smooth(formula = y ~ x, method = "lm") +
    geom_smooth(
        formula = y ~ x, 
        method = "loess", 
        linetype = "dashed", 
        color = "red", 
        fill = "red", 
        alpha = 0.1
    ) +
    labs(
        title = "Cylinders vs. Miles per Gallon",
        x = "Number of Cylinders",
        y = "Miles per Gallon"
    ) +
    theme(
        plot.title = element_text(hjust = 0.5)
    )

mtcars %>%
  ggplot(aes(x = disp, y = wt)) +
    geom_point(size = 3) +
    geom_smooth(formula = y ~ x, method = "lm") +
    geom_smooth(
        formula = y ~ x, 
        method = "loess", 
        linetype = "dashed", 
        color = "red", 
        fill = "red", 
        alpha = 0.1
    ) +
    labs(
        title = "Displacement vs. Weight",
        x = "Weight (1000 lbs)",
        y = "Displacement (cu.in.)"
    ) +
    theme(
        plot.title = element_text(hjust = 0.5)
    )
```

## Discussion
We're not really sure what is going on here.


{{< pagebreak >}}

## References
::: {#refs}
:::